---
title: 'Applied Economic Forecasting'
author: "Homework Solution Sample Template"
# date: "Today"
output: pdf_document
header-includes:
 \usepackage{float} # Fixes position of graphs
 
geometry: margin=0.8in
---

```{r setup, include=FALSE}
library(fpp2)
theme_set(theme_bw())
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_chunk$set(fig.pos = 'H') #Fixes the position of my graphs 
```

This template will provide a guide to what I anticipate that your homework solutions will look like. Please feel free to exercise your creativity when producing your solutions however. 

- Unless stated, please display the R chunk that produced your results.

- Please ensure your do a quick spell check of your document. Press **F7** on your keyboard.

- **Whenever appropriate, please refer to the output.** Please take a look at the `.Rmd` to see how I am able to:

i. Add captions to my plots, 
ii. hyperlink and reference the plots, and
iii. embed the results stored in the R chunks into my text.

# Question 1: Generating random variables

i. Generate a random normal variable, `x1`, that has 50 observations, a mean of 75, and standard deviation of 5. That is $x1\sim N(75,5^2)$. 

- Use a seed of 12345. 
- set x1 as a ts object (`x1.ts`). Declare as a quarterly variable ending December 2020.
- Plot x1.ts 

```{r x1plots, fig.align="center",tidy=TRUE, fig.height= 3, fig.cap= "Plot of X1"} 
set.seed(12345)
x1 <- rnorm(50,mean=75,sd=5)
x1.ts <- ts(x1, frequency = 4, end = c(2020,4))
autoplot(x1.ts, col = "green4") + ggtitle("Plot of x1") + labs(x ="" , y = " ")
```
 
ii. Do you notice any discernible patterns in the plot?

**The observations of x1 in Figure \ref{fig:x1plots} appear to be random with no discernible pattern.**

iii. How do the sample mean and standard deviation compare to the population values?

```{r}
meanx1 <- round(mean(x1),3)
stdx1 <- round(sd(x1),3)
```

**The random draw of 50 observations has a mean of `r meanx1` and a standard deviation of `r stdx1`. These are not too far off from their respective population values of 75 and 5, respectively.**

# Question 2: White Noise

i. Plot the ACF of this series and comment on your observations.
```{r x1acf, fig.align="center",tidy=TRUE, tidy.opts=list(width.cutoff=80), fig.cap= "ACF Plot of X1"} 
ggAcf(x1.ts, col = "blue4",lag.max = 24) + labs(title = "ACF Plot of x1") 
```

**From the plots in Figure \ref{fig:x1acf}, all the autocorrelation statistics are within the 95% significance bands. Therefore, we can conclude that the series, `x1`,  is not distinguishable from a white noise process.**

