---
title: 'Applied Economic Forecasting'
author: "Your Name Here"
date: |
    Homework #4b - Spring `r format(Sys.Date(),"%Y")` 
output: pdf_document
header-includes:
 \usepackage{float}
geometry: margin=0.8in
---

```{r setup, include=FALSE}
library(fpp2)
library(quantmod)
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.pos = 'H') 
theme_set(theme_bw()) #Feel free to change if you like
```

**Instructions**: In all cases, please ensure that your graphs and visuals have properly titles and axes labels, where necessary. For your convenience, I have posted my R markdown file on our course website so that you can open and alter as you see fit. Refer to the output, whenever appropriate, when discussing the results. **Lastly, remember that creativity (coupled with relevance) will be rewarded.**


# Forecasting the US Unemployment Rate

Between the period January 2009 -- December 2019, the U.S. unemployment rates were on the decline. We know that this has changed since the January 2020 as a result of the pandemic. 

In our analysis below, we will pull data from `FRED` using the `quantmod` package and see how well we could have forecasted the unemployment statistics for 2019 using our basic time series decomposition techniques.

(a) Using the `getSymbols` command from the `quantmod` package, import the non-seasonally adjusted monthly US unemployment (`UNRATENSA`) data from FRED. 

(b) Edit the code below to store the data from January 2010 to December 2019 and convert to a `ts` object called `unrate.ns`.

```{r, unrate.ts,eval=FALSE}
# Remember to set eval to TRUE to run!!
yourvarhere <- UNRATENSA["2010::2019"]
unrate.ns <- ts(coredata(unrate), start  = youenterstart, frequency = youenterfreq)
```

(c) Report and discuss the (i) time series plot and (ii) any seasonality and/or trend in the data. 

Based on your plot, would you agree that an additive model is appropriate? Explain.


(d) Using the `window` command, assign the values in `unrate.ns` before 2018 as a training set called `unrate.train`. Assign the values after 2018 to a variable called `unrate.test`.

(e) Using the **training set** above and a `STL` decomposition with a periodic seasonal windows, present the plot of the decomposition of the `unrate.train` series. You will find it best to store the model result first. 

**Note: Use `unrate.train[,1]` in the `stl` command. It seems to throw an error otherwise.**


(f) Produce a plot of the **seasonally adjusted** data. 


(g) Superimpose the seasonally adjusted and trend-ycle series onto the training data. 

*You will need to change your line colors as we did in class to ensure that each series is visible.*


(h) Using a `naive` model and the `forecast()` function, produce predictions for the unemployment data for 2019. *I am asking you to produce forecasts of the reseasonalized series for the next 12 months.* 
- Please store your predictions in a variable called `pred.unrate`. 
- Create an autoplot of `pred.unrate`.

(i) Now use the `naive` method within the `stlf()` function to reseasonalize and plot the results as you did above. **Ensure that you keep using the training data here.**


(j) Produce an autoplot of the test data and autolayer the prediction values (`pred.unrate[["mean"]]`). Briefly discuss the visuals here. 

***The emphasis of your discussion should be on how well this simple STL model captures the dynamics of the actual data that we tried to forecast.***
